Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-10-03 Manuscript/manuscript.tex
Simple number of contacts analysis added to MS.

In addition, we estimated relative binding affinities 
of several moieties in POPC towards \ce{Ca^{2+}}. 
\todo{Add a simple analysis using number of contacts.}
Based on the probability isodensity contours (see Fig.~\ref{fig:volmaps}), 
we estimate that the largest contribution
to the binding of \ce{Ca^{2+}} to POPC membranes comes from the phosphate group. 
Although the isodensity plots are relatively easy to interpret,
the contours shown in Fig.~\ref{fig:volmaps} cannot conclusively tell on the details
of \ce{Ca^{2+}} binding to any of the two carbonyl moieties
but their apparently lower affinity compared to phosphate oxygens.

>>>>

In addition, we estimated relative binding affinities 
of several moieties in POPC towards \ce{Ca^{2+}}. 
The dominant contribution
to the binding of \ce{Ca^{2+}} to POPC membranes comes from the phosphate group. 
Such a finding is supported by the calculated
number of contacts between \ce{Ca^{2+}} and POPC oxygen atoms.
The average number of contacts between \ce{Ca^{2+}} and any oxygen atom in POPC is 59.8, 
whereas if only phosphate oxygen atoms are considered 
the average number of contacts decreases only by a tiny amount to 57.2. 
We corroborate this finding with the probability isodensity contours in Fig.~\ref{fig:volmaps}, 
which are easier to interpret.
